\LARGE \bf {\sc underworlds}: Cascading Situation Assessment for Robots

### 2018-03-01 paper.tex
Update on Overleaf.

\author{Séverin Lemaignan$^{1}$, Yoan Sallami$^{2}$, Christopher Wallbridge$^{1}$, Aurélie Clodic$^{2}$ and Rachid Alami$^{2}$%
\thanks{$^{1}$Authors are with Centre for Robotics and Neural Systems,
        Plymouth University, Plymouth PL48AA, United Kingdom
        {\tt\small firstname.surname@plymouth.ac.uk},
	$^{2}$Authors are with LAAS-CNRS, Université de Toulouse, CNRS, Toulouse, France
        {\tt\small firstname.surname@laas.fr}}%
}

@@

\uwds is specifically inspired by geometric and temporal reasoners like {\sc Spark}
(\emph{SPAtial Reasoning \& Knowledge})~\cite{sisbot2011situation}.  {\sc Spark}
acts as a situation assessment reasoner that generates symbolic knowledge from
the geometry of the environment with respect to relations between objects,
robots and humans. It also takes into account the different perspective that
each agent has on the environment. {\sc Spark} embeds a modality-independent
geometric model of the environment that serves both as basis for the fusion of
the perception modalities and as bridge with the symbolic
layer~\cite{lemaignan2016artificial}. This geometric model is built from 3D CAD
models of the objects, furniture and robots, and full body, rigged models of
humans. It is updated at run-time by the robot's sensors.  Likewise, \uwds
embeds a grounded amodal model of the environment, updated online from the
robot's sensors (sensor fusion).

@@

\uwds is being used within the European L2TOR project~\cite{belpaeme2015l2tor} as part of a system for a large scale study with 150 children. \uwds {\tt spatial\_relations} module is used to visualise counting tasks and teach spatial words for a second language(l2). The loose coupling provided by \uwds allows for easy integration with the {\tt spatial\_relations} between either an object localisation system that would allow for use in a physical environment (Figure~\ref{fig|l2torexample}) or a virtual tablet game. As well this loose coupling facilitated development on multiple parts of the software individually across multiple international sites.

In the counting task the child is instructed to move toy animals into enclosures. The {\tt spatial\_relations} module calculates when the robots have been placed in the enclosure. The robot then teaches the children l2 words for the numbers and encourages the children to count along.

While teaching the spatial domain the

>>>>

\author{S\'everin Lemaignan$^{1}$, Yoan Sallami$^{2}$, Christopher Wallbridge$^{1}$, Aur\'elie Clodic$^{2}$ and Rachid Alami$^{2}$%
\thanks{$^{1}$Authors are with Centre for Robotics and Neural Systems,
        Plymouth University, Plymouth PL48AA, United Kingdom
        {\tt\small firstname.surname@plymouth.ac.uk},
	$^{2}$Authors are with LAAS-CNRS, Université de Toulouse, CNRS, Toulouse, France
        {\tt\small firstname.surname@laas.fr}}%
}

@@

\uwds (as well as {\sc TOASTER} (\emph{Tracking Of Agents and Spatio-TEmporal Reasoning})~\cite{milliezframework2014}) is specifically inspired by geometric and temporal reasoners like {\sc Spark}
(\emph{SPAtial Reasoning \& Knowledge})~\cite{sisbot2011situation}.{\sc Spark}
acts as a situation assessment reasoner that generates symbolic knowledge from
the geometry of the environment with respect to relations between objects,
robots and humans. It also takes into account the different perspective that
each agent has on the environment. {\sc Spark} embeds a modality-independent
geometric model of the environment that serves both as basis for the fusion of
the perception modalities and as bridge with the symbolic
layer~\cite{lemaignan2016artificial}. This geometric model is built from 3D CAD
models of the objects, furniture and robots, and full body, rigged models of
humans. It is updated at run-time by the robot's sensors.  Likewise, \uwds
embeds a grounded amodal model of the environment, updated online from the
robot's sensors (sensor fusion).

@@

\uwds is being used within the European L2TOR project~\cite{belpaeme2015l2tor} as part of a system for a large scale study with 150 children. The \uwds {\tt spatial\_relations} module is used to visualise counting tasks and teach spatial words for a second language(l2). The loose coupling provided by \uwds allows for easy integration with the {\tt spatial\_relations} between either an object localisation system that would allow for use in a physical environment (Figure~\ref{fig|l2torexample}) or a virtual tablet game. As well, this loose coupling facilitated development on multiple parts of the software individually across multiple international sites.

In the counting task the child is instructed to move toy animals into enclosures. The {\tt spatial\_relations} module calculates when the robots have been placed in the enclosure, and passes this on to another part of the system. The robot then teaches the children l2 words for the numbers and encourages the children to count along. While teaching the spatial domain the robot ask the children to move objects into positions related to other objects (e.g. put the box on the shelf). The performance can be evaluated by the {\tt spatial\_relations} module between objects. In both tasks the robot is able to provide targeted feedback on the position of an animal or object as the spatial relation is calculated rather than just attempting to fulfil a particular position criteria
